The symmetric \textit{Fermi} and eROSITA bubbles problem: A proof-of-concept study

### 2022-01-29 paper.tex
update

\begin{figure}
  \includegraphics[width=\linewidth]{figures/fig__spectrum.png}
  \caption{
      Simulated gamma-ray spectra (colored lines in top panel) of the Fermi bubbles calculated for a longitude range of\
      $|l|<10^{\circ}$ for different latitude bins.\
      The gray band represents the observational data of \citet{Ackermann2014}.\
      Simulated microwave spectra (colored lines in bottom) averaged over $|l|<10^{\circ}$, $20^{\circ}<|b|<30^{\circ}$.\
      The data point represents the \textit{WMAP} data in the 23 GHz K band and the shaded area indicates the range\
      of synchrotron spectral indices allowed for the \textit{WMAP} haze \citep{Dobler_2008}.
  }
  \label{fig__gammaRay}
\end{figure}

>>>>

\begin{figure*}
  \includegraphics[width=\linewidth]{figures/fig__spectrum.png}
  \caption{
      Simulated gamma-ray spectra (colored lines in right column) of the Fermi bubbles calculated for a longitude range of\
      $|l|<10^{\circ}$ for different latitude bins.\
      The gray band represents the observational data of \citet{Ackermann2014}.\
      Simulated microwave spectra (colored lines in left) averaged over $|l|<10^{\circ}$, $20^{\circ}<|b|<30^{\circ}$.\
      The data point represents the \textit{WMAP} data in the 23 GHz K band and the shaded area indicates the range\
      of synchrotron spectral indices allowed for the \textit{WMAP} haze \citep{Dobler_2008}.
  }
  \label{fig__gammaRay}
\end{figure*}
